Methods and Results

### 2022-10-18 ms.Rmd
Trying to sort out CI plots
Finally figured out pred. By default it doesn't require the intercept to be specified in the newmods argument. So, you can ignore this when making design matrix

p3 = ggplot(data, aes(x = SSD_lnRR, y = SMDH, size = 1/sqrt(v_SMDH), colour = Harm_type)) + 
    geom_point(alpha = 0.6) + 
      theme_classic() + 
  labs(x = "Sexual Size Dimorphism (SSD) Index", 
	     y = "SMDH",
	  size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$"),
	  colour = "Male Harm Type") +
  scale_colour_discrete(labels = c("Both", "Direct", "Indirect")) +
	guides(size = guide_legend(direction = "vertical")) +
  annotate('text', x = -0.4, y = 4.5, label = TeX(contrast3top), size = 5) +
  annotate('text', x = -0.4, y = 4.2, label = TeX(contrast3bottom), size = 5) +
  annotate('text', x = -0.4, y = 3.9, label = TeX(contrast3bottom2, italic = TRUE), size = 5) +
  geom_abline(intercept = robust_model1.3_nonZ$beta[1], slope = robust_model1.3_nonZ$beta[2]) + axis_size# Note using model1.3 for plotting because this is marginalised across Harm_type.

>>>>

predDat <- data.frame(predict(model1.5_nonZ , newmods = cbind(0, 0, seq(from = min(data$SSD_lnRR, na.rm = T), to = max(data$SSD_lnRR, na.rm = T), length.out = 100)), addx = TRUE))

p3 = ggplot(data, aes(x = SSD_lnRR, y = SMDH)) + 
    geom_point(aes(size = 1/sqrt(v_SMDH), colour = Harm_type), alpha = 0.6) + 
      theme_classic() + 
  labs(x = "Sexual Size Dimorphism (SSD) Index", 
	     y = "SMDH",
	  size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$"),
	  colour = "Male Harm Type") +
  scale_colour_discrete(labels = c("Both", "Direct", "Indirect")) +
	guides(size = guide_legend(direction = "vertical")) +
  annotate('text', x = -0.4, y = 4.5, label = TeX(contrast3top), size = 5) +
  annotate('text', x = -0.4, y = 4.2, label = TeX(contrast3bottom), size = 5) +
  annotate('text', x = -0.4, y = 3.9, label = TeX(contrast3bottom2, italic = TRUE), size = 5) +
  geom_smooth(data = predDat, aes(x = X.SSD_lnRR , y = ci.ub), method =  "lm", formula = y~x,se = FALSE,lty = "dashed", color = "black") +
  geom_smooth(data = predDat, aes(x = X.SSD_lnRR , y = ci.lb), method =  "lm", formula = y~x,se = FALSE, lty ="dashed", color = "black") +
  geom_smooth(data = predDat, aes(x = X.SSD_lnRR , y = pred), method =  "lm", formula = y~x, se = FALSE, color = "black")
  #geom_abline(intercept = robust_model1.3_nonZ$beta[1], slope = robust_model1.3_nonZ$beta[2]) + axis_size# Note using model1.3 for plotting because this is marginalised across Harm_type.
